### 2022-03-21 chapters/04-chapter-4.tex
txs auto checkin

\If(\tcc*[h]{a simple if but with a comment on the same line}){this is true}{
	we do that, else nothing\;
	\tcc{we will include other if so you can see this is possible}
	\eIf{we agree that}{
		we do that\;
	}{
		else we will do a more complicated if using else if\;
		\uIf{this first condition is true}{
			we do that\;
		}
		\uElseIf{this other condition is true}{
			this is done\tcc*[r]{else if}
		}
		\Else{
			in other case, we do this\tcc*[r]{else}
		}
	}
}

>>>>

	\If{baseline model not exist}{retrieve baseline model}
